Prag Bat Summary

### 2022-02-08 analysis/summary.Rmd
add model weights formula

ggplot()+
  geom_hline(data = p32, aes(yintercept = chance), lty = 2)+
  geom_smooth(data = p31, aes(x = age, y = mean), method = "lm", col = "black", size = 1)+
  geom_point(data = p31, aes(x = age, y = mean), alpha = .5, width = .05, height = .01)+
  geom_pointrange(data = p32, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage)))+
  facet_wrap(~task)+
  labs(x = "Age Group", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  ylim(-0.05, 1.05)+
  xlim(3,5)+
  theme_few()+
  theme(legend.position = c(.85,.2), legend.direction = "horizontal")
```
Results replicate the previous studies. The newly added match-to-sample task did not work too well in that we have no solid group-level performance above chance for the two age groups and no age effect. Reliability for the task is also unknown as it was not part of the previous studies.

@@

```{r}
# fit <- bcfa(model, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 3000, sample = 3000)
# 
# fit2 <- bcfa(model2, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 3000, sample = 3000)
# 
# fit3 <- bcfa(model3, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 3, burnin = 3000, sample = 3000)
```

```{r}
# blavCompare(fit, fit2)
# 
# blavCompare(fit, fit3)
# 
# blavInspect(fit, "lvs")
```

>>>>

ggplot()+
  geom_hline(data = p32, aes(yintercept = chance), lty = 2)+
  geom_smooth(data = p31, aes(x = age, y = mean), method = "lm", col = "black", size = 1)+
  geom_point(data = p31, aes(x = age, y = mean), alpha = .5, width = .05, height = .01)+
  geom_pointrange(data = p32, aes(x = as.numeric(as.character(subage))+.5, y = mean, ymin = ci_lower, ymax = ci_upper, col = factor(subage)))+
  facet_wrap(~task)+
  labs(x = "Age Group", y = "Proportion Correct")+
  scale_color_ptol(name = "Age")+
  ylim(-0.05, 1.05)+
  xlim(3,5)+
  theme_few()+
  theme(legend.position = c(.85,.2), legend.direction = "horizontal")
```

Results replicate the previous studies. The newly added match-to-sample task did not work too well in that we have no solid group-level performance above chance for the two age groups and no age effect. Reliability for the task is also unknown as it was not part of the previous studies.

@@

```{r}
fit <- bcfa(model, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)

saveRDS(fit, "../saves/bcfa_prag")

fit2 <- bcfa(model2, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)

saveRDS(fit2, "../saves/bcfa_single")

fit3 <- bcfa(model3, data = semd, bcontrol = list(cores = 3), target = "stan", n.chains = 4, burnin = 5000, sample = 5000)

saveRDS(fit3, "../saves/bcfa_separate")
```

```{r}
blavCompare(fit, fit2)

blavCompare(fit, fit3)

blavInspect(fit, "lvs")
```

```{r}
#model weights
w1 <- exp(-0.5*0)/(exp(-0.5*0)+exp(-0.5*6.7)+exp(-0.5*7.1)+exp(-0.5*8.9))
```
